\documentclass[12pt]{article}
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
\rhead{COMP 354}
\lhead{Diary}
\rfoot{Page \thepage}
\begin{document}
\begin{center}
    
\textbf{\textsc{DIARY}} \\
\textbf{\textsc{Ornela Bregu / ID: 26898580}} \\ 
\textbf{\textsc{Iteration 1}}
\end{center}

\begin{flushleft}    

\textbf{Date: Jan 17, 2018} \\
Time: 19:15 - 20:45 \\
Present: Every member \\
Description: First meeting during the first lab   \\

\begin{itemize}
  \item Sabrina created a list with everyone’s contact information.
  \item Assigned roles for everyone for the first iteration. I am an organiser.
  \item Agreed on three use cases for the first iteration:
  \begin{itemize}
  \item Cash Spending 
  \item Budgeting 
  \item Cards
  \end{itemize}
  \item Agreed to communicate via Discord because of its convenient features.


  \item We decided: 
\begin{itemize}
  \item To create a group on facebook. (assigned to Noemi)
  \item To post our schedule in the created group. (assigned to everyone)
  \item To post the list with contact information on facebook. (assigned to Sabrina)
  \item To create the Discord channel. (assigned to Sabrina)
  \item To create a git repository. (assigned to William)
  \end{itemize}
 \end{itemize}
   

\textbf{Date: Jan 18, 2018} \\
Time: 20:30 - 21:20 \\
Present: Every member \\
Description: First Tutorial  \\

\begin{itemize}

\item Han, Real and Theo joined our team.
\item I switched my role with Tiantian. I am a documenter now. 
\end{itemize}

\textbf{Date: Jan 19, 2018} \\
Time: 20:30 - 21:20 \\
Present: Every member \\
Description: General work  \\

\begin{itemize}

\item Tiantian and Noemi worked on the use case template and provided a general example of its format in pdf and latex.
\item Noemi started coding and proposed a possible user interface for the application. 
\item William made an explanatory video for GitHub.
\item Genevieve proposed a work plan for everyone for the first iteration.
\item Real proposed to create a Google Drive shared folder so we could work together in real-time. 
\end{itemize}


\textbf{Date: Jan 23, 2018} \\
Description: Personal work  \\
\begin{itemize}
\item  Started to get information about requirements and use cases. [08:00 - 10:20]
\item  Started to watch tutorials on latex. [13:30 - 14:10]
\item  Installed git and started to get familiar with it. Participated to a git tutorial too. [18:00 - 21:00] 
\end{itemize}


\textbf{Date: Jan 24, 2018} \\
Time: 19:15 - 20:45 \\
Present: Every member except Noemi \\
Description: Lab 2  \\

\begin{itemize}
\item Discussed again about the features of our application and made some changes on the functionalities. 
\item Real made a kanban on Trello to keep track of our tasks. 
\item I was assigned the documentation for the Cash Spending Use Case.
\end{itemize}


\textbf{Date: Jan 27, 2018} \\
Description: General work  \\
\begin{itemize}
\item I started to work on the user requirements document and modified the given template on latex according to our project. Added comments about things we needed for every section and defined the purpose and business goals of our application. [09:00 - 09:30]
\item Committed the Cash Spending Use Case on GitHub. 
\item Tiantian and Han worked on Domain Model and Use Case diagram.
\end{itemize}

\textbf{Date: Jan 31, 2018} \\
Time: 19:15 - 20:45 \\
Present: Every member except William \\
Description: Lab 3/ Demo  
\newline

The demonstration of our work until now took place during the lab. According to Teacher Assistant :
\begin{itemize}
\item Use case diagram and domain model need some improvements. 
\item The user requirements document needs to be finished.
\item A database implementation should be done. 
\end{itemize}

\textbf{Date: Feb 3, 2018} \\
Time: 10:00 - 13:00 \\
Description: Personal work  \\
\begin{itemize}
\item Improved my Cash Spending use case.
\item Improved the use case diagram.
\item Posted some tips and guidelines on creating good use cases on Discord.
\item Updated the user requirements documents with a system overview and some functional requirements. 
\end{itemize}


\textbf{Date: Feb 8, 2018} \\
Time: 09:00 - 11:15, 15:00 - 17:15 \\
Description: Personal work  \\
\begin{itemize}

\item Edited and finalized the domain model.[09:00 - 10:15]
\item Edited the user requirements document, added all the use cases and the domain model diagram. [11:30 - 13:15]
\item Worked on non-functional requirements. [15:00 - 17:15] 
\item Discussed with Dong-Son and Ashesh after the lecture about the last things left to be done.
\end{itemize}

\textbf{Date: Feb 9, 2018} \\
Time: 10:45 - 11:30 \\
Description: Personal work  \\
\begin{itemize}

\item Finished and added the non-functional requirements on the requirement document.
\item Fixed some layout and content problems.

\end{itemize}
\end{flushleft}
\end{document}
